Patient movements

### 2024-04-18 analysis/patient-tracking.Rmd
Minor changes to visualizations

save_plot(
  time_pl,
  pdf_file = "results/data/no-people-over-time.png",
  w = 8, h = 6
)
```

@@

save_plot(
  spatial_pl,
  pdf_file = "results/data/no-people-spatial.png",
  w = 8, h = 6
)
```

>>>>

save_plot(
  time_pl,
  pdf_file = "results/data/no-people-over-time.png",
  w = 8, h = 8
)
```

@@

save_plot(
  spatial_pl,
  pdf_file = "results/data/no-people-spatial.png",
  w = 8, h = 8
)
```
